Download data

### 2024-05-07 scripts/subsetDataforCrews.Rmd
prototype to write sdm polys and points together

ptest <- mask(ptest, blm_surf_sub)
plot(ptest)

a <- lapply(X = spp_needed_test[1], FUN = empiricalSTZ_writer, seed_zones = seed_zones, pSTZs = ptest)

b <- vect(spp_needed_test[[1]][,'path_basins'])

ob <- terra::mask(b, ptest)

plot(a[["Aristida_purpurea"]])
```

>>>>

ptest <- mask(ptest, blm_surf_sub)
trim(ptest)
plot(ptest)

a <- lapply(X = spp_needed_test[1], FUN = empiricalSTZ_writer, 
            seed_zones = seed_zones, pSTZs = ptest) # 24 pts, 245 polys
